---
title: "Indian Food Cookbook"
author: "Emily, Ellyn, Rachel, Gabe"
date: "2/17/2022"
output: html_notebook
html_document: 
    theme: spacelab
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Background of Project

Welcome to the Exploring India Cookbook, this an e-cook book that will allow you to select different dishes you would like to make depending on your diet, amount of time you have, the course you would like to make, or based on the region. 

This project is separated into three parts:
Section 1: Loading and Cleaning the Data
Section 2: Questions about the data
Section 3: Exploring India Cookbook App


##Section 1:

This section illustrates how we loaded the data, assessed the data structure, and cleaned the data. 
_Load Library_

```{r}
library(tidyverse)
library(RColorBrewer)
library(paletteer)
library(janitor)
library(here)
library(naniar)
library(gapminder)
```


1. Load the data. 
```{r}
##indian_food<- read_csv(here("indian_food_data.csv"))%>% clean_names()

```
2. Structure of the data. 
```{r}
glimpse(indian_food)
```

```{r}
summary(indian_food)
```
What are the variables? 
```{r}
names(indian_food)
```

Dealing with NA's

_NA's in data is symbolized by a "-1"_
```{r}
indian_food<-indian_food%>%
  na_if("-1")
```

Counting Number of NA's
```{r}
naniar::miss_var_summary(indian_food)

```
_Split Ingredients Into Their Own Row_

We noticed that the ingredients were listed in one row, so we separated them into their own rows. 

```{r}
indian_food<-indian_food%>%
  mutate_all(tolower)%>%
  transform(ingredients=str_split(ingredients,","))%>%
  unnest(ingredients)
indian_food
```

Adding Total Cook Time column which combines cook time and prep time. 
```{r}
indian_food<-indian_food%>%
  mutate(total_cook_time=as.numeric(cook_time)+as.numeric(prep_time))
indian_food
```


##Section Two: Questions about the data.
1. Does it take more or less time to cook vegetarian versus non-vegetarian dishes?
```{r}
indian_food_together <- readr::read_csv("/Users/ellyn/Desktop/BIS15W2022_Group2/indian_food_data.csv")

indian_food_together <-indian_food_together%>%
  na_if("-1")

indian_food_together <- indian_food_together%>%
  mutate(total_cook_time=as.numeric(cook_time)+as.numeric(prep_time))

indian_food_together
```


```{r}
indian_food_together %>% 
  filter(!is.na(total_cook_time)) %>% 
  group_by(diet) %>% 
  summarize(mean_total_time = mean(total_cook_time))
```

```{r}
v_nv <- indian_food_together %>% 
    filter(!is.na(total_cook_time)) %>% 
  group_by(diet) %>% 
  summarize(mean_total_time = mean(total_cook_time),
            min_total_time = min(total_cook_time),
            max_total_time = max(total_cook_time))
v_nv
```


```{r}
v_nv_long <- v_nv%>%
  pivot_longer(-diet, names_to ="time", values_to="cook_time")
v_nv_long
```
```{r}
v_nv_plot <- v_nv_long %>% 
  ggplot(aes(x=time, y=cook_time, fill=diet))+geom_col(position = "dodge")
v_nv_plot
```
2. For each diet, vegetarian and non-vegetarian, identify which dish takes the most and least amount of total cook time, prep time, and cook time.
```{r}
indian_food_together %>% 
  filter(diet == "non vegetarian") %>% 
  filter(total_cook_time == 20) 

indian_food_together %>% 
  filter(diet == "non vegetarian") %>% 
  filter(total_cook_time == 270) 
```


```{r}
indian_food_together %>% 
  filter(diet == "vegetarian") %>% 
  filter(total_cook_time == 730)

indian_food_together %>% 
  filter(diet == "vegetarian") %>% 
  filter(total_cook_time == 10)
```


3. What is the relationship between flavor and diet (i.e. is there more spicy dishes in non-vegetarian compared to vegetarian?)
```{r}

```

4. Which ingredient is used the most for each region/state?
```{r}

```

5. What ingredient is used the most out of all the courses? What is the % of ingredient in all recipes. 
```{r}

```

6. What diet is more associated with which region/state?
```{r}

```

7. What flavor profile is more associated with which region/state?
```{r}

```

8. What is the population growth, GDP growth, and life expectancy of India (use gapminder data)?
```{r}

```

9. What is the distribution of courses (e.g. main courses, snacks, dessert)?
```{r}

```


10. Does agriculture by region have an impact on diet?

## We started by uploading the data on agriculture and cleaning it up.
```{r}
agriculture <- readr::read_csv("/Users/ellyn/Desktop/BIS15W2022_Group2/agriculture.csv")

agriculture <- janitor::clean_names(agriculture)

agriculture <- agriculture %>% 
  mutate_all(tolower)

agriculture <- agriculture %>% 
  select("crop", "state")

agriculture
```

## Both datasets shared a similar region column, which we used to merge the two.
```{r}
agr_diet <- full_join(indian_food_together, agriculture, by="state")
agr_diet
```

## Does the specialty crop have an impact on the total cook time?
```{r}
agr_diet %>% 
  filter(crop!="NA") %>% 
  filter(total_cook_time!="NA") %>% 
  ggplot(aes(x=crop, y=total_cook_time, fill=crop))+geom_boxplot(color="white", alpha=.4, na.rm = TRUE)+
  geom_violin(alpha=.7, na.rm=TRUE)+ coord_flip()
```



```{r}

ui <- basicPage(
  h2("Indian Food Cookbook"),
  DT::dataTableOutput("mytable")
)

server <- function(input, output) {
  output$mytable = DT::renderDataTable({
    indian_food
  })
}
  

```

```{r}
getwd()
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:
>>>>>>> bef485c67e24d246376fdc1086dd9c843c4d1b72

```

